Garbage Collection Evaluation Infrastructure\\ for the Cog VM

### 2018-06-20 paper.tex
add result description for large objects bench

We built three benchmarks out of the potential configurations:
\begin{itemize}
\item \emph{FragmentedHeap:} First, objects are allocated on the heap, and some of them are released, leading to potential memory fragmentation. Then, new objects with a minimum size greater than the new free chunks sizes are allocated.
\item \emph{LargeObjects:} Only large objects with a size greater than 0xFFFF \sk{put real size in Kb here} are allocated on the heap.
\item \emph{Data0bjects:} The majority of objects that will be allocated on the heap will be Data objects, which will only contains one-byte-sized integers of a specific size in this benchmark  
\end{itemize}

@@

\subsection{Mark-Compact}

@@

\paragraph{FragmentedHeap.} 
allocate n objects of size x, release half of them, and reallocate n/2 objects of size y>x. Compare the performance (time spent in full GC, scavenges, compacting, and execution time) for both Mark-Sweep and Mark-Compact
\begin{itemize}
\item impact on memory size and numbers of segments
\item impact on execution time 
\end{itemize}
\paragraph{LargeObjects.}
allocate objects larger than 0xffff. Compare two VMs with different number of segments.
\begin{itemize}
\item impact on memory size 
\item impact on number of scavenges and number of full GC's
\end{itemize}
\paragraph{Data0bjects.}
 allocate a lot of data objects (90\% of all allocated objects during the bench). Compare for Mark-Sweep and Mark-Compact
\begin{itemize}
\item impact on memory size
\item impact on overall time (full gc, compaction time)
\end{itemize}

>>>>

We built three benchmarks out of the potential configurations:
\begin{itemize}
\item \emph{FragmentedHeap:} First, objects are allocated on the heap, and some of them are released, leading to potential memory fragmentation. Then, new objects with a minimum size greater than the new free chunks sizes are allocated.
\item \emph{LargeObjects:} Only large objects with a size greater than 65535 32-bits machines words are allocated on the heap. These objects are allocated directly in the old space.
\item \emph{Data0bjects:} The majority of objects that will be allocated on the heap will be Data objects, which will only contains one-byte-sized integers of a specific size in this benchmark  
\end{itemize}

@@

\subsection{Mark-Compact} \label{sec:refmc}

@@

\paragraph{FragmentedHeap.} 
allocate n objects of size x, release half of them, and reallocate n/2 objects of size y>x. Compare the performance (time spent in full GC, scavenges, compacting, and execution time) for both Mark-Sweep and Mark-Compact
\begin{itemize}
\item impact on memory size and numbers of segments
\item impact on execution time 
\end{itemize}
\paragraph{LargeObjects.} The LargeObjects benchmark allocates objects larger than 65535 32-bits machine words. The time spent in scavenges is therefore lower. Allocating large objects has an impact on the number operations of memory growing and shrinking, which can be lowered by tuning the associated parameters in the VM. 
\paragraph{Data0bjects.}
 allocate a lot of data objects (90\% of all allocated objects during the bench). Compare for Mark-Sweep and Mark-Compact
\begin{itemize}
\item impact on memory size
\item impact on overall time (full gc, compaction time)
\end{itemize}
